Target Speaker Extraction using Discrete Representations from Self-Supervised Models and Language Models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-04 src/paper.tex
update

\section{Method}
Our model consists of three stages: encoding, modeling, and decoding. The encoder and decoder are 
pretrained models freezed during training. For the encoding stage, we use multiple layers of WavLM 
and publicly available Kmeans 
models in \cite{dasb} to produce the discretized tokens. We use a special concatenation 
strategy to encode the mixture speech. For decoders, we use the scalable HiFi-GAN available in 
\cite{dasb} to reconstruct the audio from discretized tokens. Our main focus is on the
modeling stage. We apply an attention embedding mechanism to embed discrete tokens from different 
layers into one single embedding. Encoder-only LM and linear classifier is applied afterwards to optimize the likelihood of probability 
distribution of the clean tokens.

@@

>>>>

\section{Method}
Our model consists of three stages: encoding, modeling, and decoding. The encoder and decoder are 
pretrained models and they are freezed during training. For the encoding stage, we use multiple layers of WavLM 
and publicly available Kmeans 
models in \cite{dasb} to produce the discretized tokens. We use a special concatenation 
strategy to encode the mixture speech. For decoders, we use the scalable HiFi-GAN available in 
\cite{dasb} to reconstruct the audio from discretized tokens. Our main focus is on the
modeling stage. We apply an attention embedding mechanism to embed discrete tokens from different 
layers into one single embedding. Encoder-only LM and linear classifier is applied afterwards to optimize the likelihood of probability 
distribution of the clean tokens.

@@

\section{Experiments}

\subsection{Datasets and evaluation metrics}

\subsubsection{Training sets}
We use the pretrained WavLM Large \cite{wavlm} and it is freezed during training. The Kmeans tokenizer is trained on the
